J-ReCoVer: Java Reducer Commutativity Verifier

### 2018-11-11 draft.tex
conclusion

The current version of J-Recover shares similar limitation with SMT-based software verification tools.
We use SMT theory of integer and real number arithmetics as the reasoning tool. In this implementation. We do not handle more advanced data-types such as string and floating point. The problem of variable overflow is not handled by this tool. In fact, if we consider all possible inputs of a reducer, almost all reducer programs will run into the problem of overflow. Even the basic example that computes the sum of all input values, overflow can occur when a list contains two maximal 64-bit integer values is used as the input. Nevertheless, such example might not be of the interests of MapReduce programmers, who usually care only about the data set they want to analyze. We are planing to build another tool that estimates a safe bound of data size such that overflow will not occur. The programmer can than check if their data set fits the computed bound and use lager data type in the program when needed. So overflow will not occurs in the data set of interests.

>>>>

The current version of J-Recover shares similar limitation with SMT-based software verification tools.
We use SMT theory of integer and real number arithmetics as the reasoning tool. In this implementation. We do not handle more advanced data-types such as string and floating point. The problem of variable overflow is not handled by this tool. In fact, if we consider all possible inputs of a reducer, almost all reducer programs will run into the problem of overflow. Even the basic example that computes the sum of all input values, overflow can occur when a list contains two maximal 64-bit integer values is used as the input. Nevertheless, such example might not be of the interests of MapReduce programmers, who usually care only about the data set they want to analyze. We are planing to build another tool that estimates a safe bound of data size such that overflow will not occur if data size is within bound. The programmer can then check if their data set fits in the computed bound and switch to use lager data type in the program when needed. So overflow will not occurs in the data set of interests.
